---
title: "Linear Model"
author: "Nalleli Tapia"
date: "23 Oct 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
myData = read.csv('RawData.csv')
```


#first model
SIMS is a function of ARM

```{r}
model1 = lm(SIMS~ARM, data=myData)
summary(model1)
```

predict SIMS for ARM = 88

```{r}
#predSIMS = -4.096 +0.055*88
#print(predSIMS)

x = data.frame(GRIP=94, ARM=88)
predSIMS = predict.lm(model1, x)
print(predSIMS)
```

prediction interval:
```{r}
predict(model1, x, interval="predict", level=0.95)
```

# second model SIMS is a function of GRIP

```{r}
model2 = lm(SIMS~GRIP, data=myData)
summary(model2)
```

predict SIMS for GRIP = 94

```{r}
predictSIMS2 = predict.lm(model2,x)
print(predictSIMS2)
```

# third model SIMS is a function of GRIP + ARM

```{r}
model3 = lm(SIMS~GRIP+ARM, data=myData)
summary(model3)
```

predict SIMS for ARM=88 and GRIP=94

```{r}
predictSIMS3 = predict.lm(model3, x)
print(predictSIMS3)
```

prediction interval:

```{r}
predict(model1, x, interval="predict")
```

prediction interval for model3

comparison for models 1 and 3

```{r}
anova(model1,model3)
```

$h_0$: no difference in the models  
$H_A$: there is a difference in the models  

Since the pvalue is 4.994e-06. We reject the known hypothesis, there is a difference between model 1 and 3.
Model 3 is a better fit than model 1. Model 3 has a smaller sum of residual sums of square than model 1.